ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
Clarify RCM properties and other properties in PyKED
Work on #36

%====================================================================
\section{PyKED architecture}\label{sec:pyked-architecture}
%
\pk{} is a Python package that provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

@@

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole percent|,
    \yabox|mole fraction|, or \yabox|mass fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole percent'|,
    \pybox|'mole fraction'|, or \pybox|'mass fraction'|
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

If the \ck{} file encodes an RCM experiment, there are several specialized fields that can be
included.

\begin{itemize}
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: The duration of the compression stroke
    \item \pybox|compressed_temperature|: The estimated reactor temperature at the end of the
    compression stroke
    \item \pybox|compressed_pressure|: The measured reactor pressure at the end of the compression
    stroke
\end{itemize}

>>>>

%====================================================================
\section{PyKED Architecture}\label{sec:pyked-architecture}
%
\pk{} is a Python package that provides the reference implementation
of the interface to \ck{} files~\autocite{PyKED}. \pk{} reads \ck{} files, validates
their structure and content, and allows the user to interact with the data contained
in the \ck{} file.

@@

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole percent|,
    \yabox|mole fraction|, or \yabox|mass fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole percent'|,
    \pybox|'mole fraction'|, or \pybox|'mass fraction'|
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
\end{itemize}
%
Other instance attributes are stored as instances of the \pybox|Quantity| class from the
Pint \autocite{Grecco2016} package, possibly with an associated uncertainty. These include the
\pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|, \pybox|pressure_rise|,
\pybox|compression_time|, \pybox|compressed_temperature|, and \pybox|compressed_pressure|
attributes, each of which represents the similarly-named field in the \ck{} schema.
